### 2020-04-18 system-model.tex
:pencil: WSR-E region
:pencil: Fix notation
:pencil: Fix power constraints

	\begin{subsection}{Transmitted Signal}
		\begin{subsubsection} {Modulated Information Waveform}
			Assume the carrier are evenly spaced with equal bandwidth $B_s$ such that the frequency of the $n$-th subband is $f_n=f_0+(n-1){\Delta}{f}$ ($n=1,\dots,N$). The information symbol $\tilde{x}_{I,k,n}\sim\mathcal{CN}(0,1)$ of user $k$ over subband $n$ is a capacity-achieving i.i.d. Circular Symmetric Complex Gaussian (CSCG) variable with zero mean and unit variance. Therefore, the baseband (BB) transmit information signal at subband $n$ can be expressed as
			\begin{equation}\label{eq:x_{I,n}(t)}
				x_{I,n}(t)=\sum_{k=1}^K{w_{I,k,n}\tilde{x}_{I,k,n}(t)}
			\end{equation}
			where $w_{I,k,n}$ is the corresponding information weight. Let $\boldsymbol{W}_I=[\boldsymbol{w}_{I,1},\dots,\boldsymbol{w}_{I,N}]=[\boldsymbol{w}_{I,1}^T,\dots,\boldsymbol{w}_{I,K}^T]^T \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{I,n}=[w_{I,1,n},\dots,w_{I,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{w}_{I,k}=[w_{I,k,1},\dots,w_{I,k,N}] \in \mathbb{C}^{1 \times N}$. On top of this, the RF transmit information waveform at time $t$ writes as
			% Let $\boldsymbol{W}_I=[\boldsymbol{w}_{I,1},\dots,\boldsymbol{w}_{I,N}] \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{I,n}=[w_{I,1,n},\dots,w_{I,K,n}]^T \in \mathbb{C}^{K \times 1}$.
			\begin{equation}\label{eq:x_I(t)}
				\begin{split}
					x_I(t)
					&=\sum_{n=1}^N{x_{I,n}(t){e^{j2{\pi}{f_n}{t}}}}\\
					&=\sum_{k=1}^K\sum_{n=1}^N{w_{I,k,n}\tilde{x}_{I,k,n}(t){e^{j2{\pi}{f_n}{t}}}}
					% &=\Re\left\{\sum_{n=1}^N{x_{I,n}(t){e^{j2{\pi}{f_n}{t}}}}\right\}\\
					% &=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{w_{I,k,n}\tilde{x}_{I,k,n}(t){e^{j2{\pi}{f_n}{t}}}}\right\}
				\end{split}
			\end{equation}
		\end{subsubsection}

		\begin{subsubsection}{Unmodulated Power Waveform}
			As suggested in \cite{Clerckx2018b,Clerckx2016a}, we use deterministic multisine waveform to boost the harvested energy. It has no randomness over time such that the baseband transmit power signal at subband $n$ is
			\begin{equation}\label{eq:x_{P,n}}
				x_{P,n}=\sum_{k=1}^K{w_{P,k,n}}
			\end{equation}
			where $w_{P,k,n}$ is the corresponding power weight. Let $\boldsymbol{W}_P=[\boldsymbol{w}_{P,1},\dots,\boldsymbol{w}_{P,N}]=[\boldsymbol{w}_{P,1}^T,\dots,\boldsymbol{w}_{P,K}^T]^T \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{P,n}=[w_{P,1,n},\dots,w_{P,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{w}_{P,k}=[w_{P,k,1},\dots,w_{P,k,N}] \in \mathbb{C}^{1 \times N}$. Then, the transmit power signal at time $t$ is given by
			\begin{equation}\label{eq:x_P(t)}
				\begin{split}
					x_P(t)
					&=\sum_{n=1}^N{x_{P,n}{e^{j2{\pi}{f_n}{t}}}}\\
					&=\sum_{k=1}^K\sum_{n=1}^N{w_{P,k,n}{e^{j2{\pi}{f_n}{t}}}}
					% &=\Re\left\{\sum_{n=1}^N{x_{P,n}{e^{j2{\pi}{f_n}{t}}}}\right\}\\
					% &=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{w_{P,k,n}{e^{j2{\pi}{f_n}{t}}}}\right\}
				\end{split}
			\end{equation}
		\end{subsubsection}

@@

	\begin{subsection}{Received Signal}
		The RF signal received by user $k$ captures the contribution of information and power waveforms through both direct and reflective links as
		\begin{equation}\label{eq:y_k(t)}
			y_k(t)=\sum_{j=1}^K\sum_{n=1}^N(w_{I,j,n}\tilde{x}_{I,j,n}+w_{P,j,n})h_{k,n}{e^{j2{\pi}{f_n}{t}}}
		\end{equation}
		with the information and power components of
		\begin{equation}\label{eq:y_{I,k}(t)}
			y_{I,k}(t)=\sum_{j=1}^K\sum_{n=1}^N{w_{I,j,n}\tilde{x}_{I,j,n}}h_{k,n}{e^{j2{\pi}{f_n}{t}}}
		\end{equation}
		\begin{equation}\label{eq:y_{P,k}(t)}
			y_{P,k}(t)=\sum_{j=1}^K\sum_{n=1}^N{w_{P,j,n}}h_{k,n}{e^{j2{\pi}{f_n}{t}}}
		\end{equation}

@@

	\begin{subsection}{Information Decoder}
		One major benefit of using proposed waveform is that the deterministic power term $y_{P,k}(t)$ bears no information and creates no interference to the modulated information term $y_{I,k}(t)$. Hence, each user treats the information signals from other users as interference such that the SINR at subband $n$ of user $k$ is
		\begin{equation}\label{eq:gamma_{k,n}}
			\gamma_{k,n}=\frac{(1-\rho)(w_{I,k,n}h_{k,n})(w_{I,k,n}h_{k,n})^*}{\sum_{j=1,j{\ne}k}^K{(1-\rho)(w_{I,j,n}h_{I,k,n})(w_{I,j,n}h_{I,k,n})^*+\sigma_n^2}}
		\end{equation}
		where $\sigma_n^2$ is the sum variance of the Gaussian noise at the RF-band and those introduced during the RF-to-BB conversion on subband $n$. Therefore, the achievable rate of user $k$ is expressed as
		\begin{equation}\label{eq:R_k}
			R_k(\boldsymbol{W}_I,\boldsymbol{\Theta},\rho)=\sum_{n=1}^N{\log_2(1+\gamma_{k,n})}
		\end{equation}
		A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:R_k} is always achievable with or without waveform cancellation, through either subtracting the deterministic power component or constructing a translated codebook.
	\end{subsection}

@@

				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{(w_{I,j_1,n}h_{k,n})(w_{I,j_2,n}h_{k,n})^*}\label{eq:E{A{y_{I,k}**2}}}                                                                                                                                                                        \\

@@

				 & =\frac{3}{4}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(w_{I,{j_1},{n_1}}h_{k,{n_1}})(w_{I,{j_2},{n_2}}h_{k,{n_2}})(w_{I,{j_3},{n_3}}h_{k,{n_3}})^*(w_{I,{j_4},{n_4}}h_{k,{n_4}})^*}                       \\

@@

				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{(w_{P,j_1,n}h_{k,n})(w_{P,j_2,n}h_{k,n})^*}                                                                                                                                                                                                   \\

@@

				 & =\frac{3}{8}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(w_{P,{j_1},{n_1}}h_{k,{n_1}})(w_{P,{j_2},{n_2}}h_{k,{n_2}})(w_{P,{j_3},{n_3}}h_{k,{n_3}})^*(w_{P,{j_4},{n_4}}h_{k,{n_4}})^*}                       \\

@@

\begin{section}{Problem Formulation}
	In this section, we first define the weighted sum rate-energy (WSR-E) region then formulate waveform and IRS optimization problems.
	\begin{subsection}{Weighted Sum Rate-Energy Region}
		We define the achievable WSR-E region as
		\begin{equation}
			C_{R-I}(P) \triangleq \left\{(R,I):R\le\sum_{k=1}^K{u_{I,k}R_k},I\le\sum_{k=1}^K{u_{P,k}i_k,?}\right\}
		\end{equation}
		where $u_{I,k},u_{P,k}$ denote the information and power priority of user $k$.
	\end{subsection}
\end{section}

>>>>

	\begin{subsection}{Transmitted Signal}
		\begin{subsubsection} {Modulated Information Waveform}
			Assume the carrier are evenly spaced with equal bandwidth $B_s$ such that the frequency of the $n$-th subband is $f_n=f_0+(n-1){\Delta}{f}$ ($n=1,\dots,N$). The information symbol $\tilde{x}_{I,k,n}\sim\mathcal{CN}(0,1)$ of user $k$ over subband $n$ is a capacity-achieving i.i.d. Circular Symmetric Complex Gaussian (CSCG) variable with zero mean and unit variance. Therefore, the baseband (BB) transmit information signal at subband $n$ can be expressed as
			\begin{equation}\label{eq:x_{I,n}(t)}
				x_{I,n}(t)=\sum_{k=1}^K{w_{I,k,n}\tilde{x}_{I,k,n}(t)}
			\end{equation}
			where $w_{I,k,n}$ is the corresponding information weight. Let $\boldsymbol{W}_I=[\boldsymbol{w}_{I,1},\dots,\boldsymbol{w}_{I,N}]^T \in \mathbb{C}^{N \times K}$ with $\boldsymbol{w}_{I,n}=[w_{I,1,n},\dots,w_{I,K,n}]^T \in \mathbb{C}^{K \times 1}$. On top of this, the overall frequency weight is denoted as $w_{I,n}=\sum_k{w_{I,k,n}}$ and collected into $\boldsymbol{w}_I=[w_{I,1},\dots,w_{I,N}]^T \in \mathbb{C}^{N \times 1}$. The RF transmit information waveform at time $t$ writes as
			% Let $\boldsymbol{W}_I=[\boldsymbol{w}_{I,1},\dots,\boldsymbol{w}_{I,N}]=[\boldsymbol{w}_{I,1}^T,\dots,\boldsymbol{w}_{I,K}^T]^T \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{I,n}=[w_{I,1,n},\dots,w_{I,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{w}_{I,k}=[w_{I,k,1},\dots,w_{I,k,N}] \in \mathbb{C}^{1 \times N}$.
			% Let $\boldsymbol{W}_I=[\boldsymbol{w}_{I,1},\dots,\boldsymbol{w}_{I,N}] \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{I,n}=[w_{I,1,n},\dots,w_{I,K,n}]^T \in \mathbb{C}^{K \times 1}$.
			\begin{equation}\label{eq:x_I(t)}
				\begin{split}
					x_I(t)
					&=\sum_{n=1}^N{x_{I,n}(t){e^{j2{\pi}{f_n}{t}}}}\\
					&=\sum_{k=1}^K\sum_{n=1}^N{w_{I,k,n}\tilde{x}_{I,k,n}(t){e^{j2{\pi}{f_n}{t}}}}
					% &=\Re\left\{\sum_{n=1}^N{x_{I,n}(t){e^{j2{\pi}{f_n}{t}}}}\right\}\\
					% &=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{w_{I,k,n}\tilde{x}_{I,k,n}(t){e^{j2{\pi}{f_n}{t}}}}\right\}
				\end{split}
			\end{equation}
		\end{subsubsection}

		\begin{subsubsection}{Unmodulated Power Waveform}
			As suggested in \cite{Clerckx2018b,Clerckx2016a}, we use deterministic multisine waveform to boost the harvested energy. It has no randomness over time such that the baseband transmit power signal at subband $n$ is
			\begin{equation}\label{eq:x_{P,n}}
				x_{P,n}=\sum_{k=1}^K{w_{P,k,n}}
			\end{equation}
			where $w_{P,k,n}$ is the corresponding power weight. Let $\boldsymbol{W}_P=[\boldsymbol{w}_{P,1},\dots,\boldsymbol{w}_{P,N}]^T \in \mathbb{C}^{N \times K}$ with $\boldsymbol{w}_{P,n}=[w_{P,1,n},\dots,w_{P,K,n}]^T \in \mathbb{C}^{K \times 1}$. Similarly, the overall frequency weight is denoted as $w_{P,n}=\sum_k{w_{P,k,n}}$ and collected into $\boldsymbol{w}_P=[w_{P,1},\dots,w_{P,N}]^T \in \mathbb{C}^{N \times 1}$. The transmit power signal at time $t$ is given by
			% Let $\boldsymbol{W}_P=[\boldsymbol{w}_{P,1},\dots,\boldsymbol{w}_{P,N}]=[\boldsymbol{w}_{P,1}^T,\dots,\boldsymbol{w}_{P,K}^T]^T \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{P,n}=[w_{P,1,n},\dots,w_{P,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{w}_{P,k}=[w_{P,k,1},\dots,w_{P,k,N}] \in \mathbb{C}^{1 \times N}$.
			\begin{equation}\label{eq:x_P(t)}
				\begin{split}
					x_P(t)
					&=\sum_{n=1}^N{x_{P,n}{e^{j2{\pi}{f_n}{t}}}}\\
					&=\sum_{k=1}^K\sum_{n=1}^N{w_{P,k,n}{e^{j2{\pi}{f_n}{t}}}}
					% &=\Re\left\{\sum_{n=1}^N{x_{P,n}{e^{j2{\pi}{f_n}{t}}}}\right\}\\
					% &=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{w_{P,k,n}{e^{j2{\pi}{f_n}{t}}}}\right\}
				\end{split}
			\end{equation}
		\end{subsubsection}

@@

	\begin{subsection}{Received Signal}
		The RF signal received by user $k$ captures the contribution of information and power waveforms through both direct and reflective links as
		\begin{equation}\label{eq:y_k(t)}
			y_k(t)=\sum_{j=1}^K\sum_{n=1}^N{h_{k,n}}(w_{I,j,n}\tilde{x}_{I,j,n}+w_{P,j,n}){e^{j2{\pi}{f_n}{t}}}
		\end{equation}
		with the information and power components of
		\begin{equation}\label{eq:y_{I,k}(t)}
			y_{I,k}(t)=\sum_{j=1}^K\sum_{n=1}^N{h_{k,n}w_{I,j,n}\tilde{x}_{I,j,n}}{e^{j2{\pi}{f_n}{t}}}
		\end{equation}
		\begin{equation}\label{eq:y_{P,k}(t)}
			y_{P,k}(t)=\sum_{j=1}^K\sum_{n=1}^N{h_{k,n}w_{P,j,n}}{e^{j2{\pi}{f_n}{t}}}
		\end{equation}

@@

	\begin{subsection}{Information Decoder}
		One major benefit of using proposed waveform is that the deterministic power term $y_{P,k}(t)$ bears no information and creates no interference to the modulated information term $y_{I,k}(t)$. Hence, each user treats the information signals from other users as interference such that the SINR at subband $n$ of user $k$ is
		\begin{equation}\label{eq:gamma_{k,n}}
			\gamma_{k,n}=\frac{(1-\rho)(h_{k,n}w_{I,k,n})(h_{k,n}w_{I,k,n})^*}{\sum_{j=1,j{\ne}k}^K{(1-\rho)(h_{k,n}w_{I,j,n})(h_{k,n}w_{I,j,n})^*+\sigma_n^2}}
		\end{equation}
		where $\sigma_n^2$ is the sum variance of the Gaussian noise at the RF-band and those introduced during the RF-to-BB conversion on subband $n$. Therefore, the achievable rate of user $k$ is expressed as
		\begin{equation}\label{eq:R_k}
			R_k(\boldsymbol{W}_I,\boldsymbol{\Theta},\rho)=\sum_{n=1}^N{\log_2(1+\gamma_{k,n})}
		\end{equation}
		A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:R_k} is always achievable with or without waveform cancellation, through either subtracting the deterministic power component or constructing a translated codebook.
	\end{subsection}

@@

				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{(h_{k,n}w_{I,j_1,n})(h_{k,n}w_{I,j_2,n})^*}\label{eq:E{A{y_{I,k}**2}}}                                                                                                                                                                        \\

@@

				 & =\frac{3}{4}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{I,{j_1},{n_1}})(h_{k,{n_2}}w_{I,{j_2},{n_2}})(h_{k,{n_3}}w_{I,{j_3},{n_3}})^*(h_{k,{n_4}}w_{I,{j_4},{n_4}})^*}                       \\

@@

				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{(h_{k,n}w_{P,j_1,n})(h_{k,n}w_{P,j_2,n})^*}                                                                                                                                                                                                   \\

@@

				 & =\frac{3}{8}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{P,{j_1},{n_1}})(h_{k,{n_2}}w_{P,{j_2},{n_2}})(h_{k,{n_3}}w_{P,{j_3},{n_3}})^*(h_{k,{n_4}}w_{P,{j_4},{n_4}})^*}                       \\

@@

\begin{section}{Problem Formulation}
	In this section, we first define the weighted sum rate-energy (WSR-E) region then formulate waveform and IRS optimization problems.
	\begin{subsection}{Weighted Sum Rate-Energy Region}
		We define the achievable WSR-E region as
		\begin{equation}
			\begin{split}
				C_{R-I}(P)
				&\triangleq \biggl\{(R,I):R\le\sum_{k=1}^K{u_{I,k}R_k},I\le\sum_{k=1}^K u_{P,k}z_k,\\
				&\quad \frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P}){\le}P\biggr\}
				% &\quad \frac{1}{2}\left(\Vert{\boldsymbol{W}_I}\Vert_F^2+\Vert{\boldsymbol{W}_P}\Vert_F^2\right){\le}P\biggr\}
			\end{split}
		\end{equation}
		where $u_{I,k},u_{P,k}$ denote the information and power weight of user $k$.
	\end{subsection}
\end{section}
